Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
review comment
coefficient representation (first half)

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the controller's coefficients;  
similarly $\vec{b}$ and $\vec{a}$ encompass the plant's coefficients;  
and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfil this property in our implementation).

The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
\begin{equation}
\Delta{\vec{p}}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\label{eq:uncertainty}
\end{equation}

A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$. The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

@@

In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

@@

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if: 
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
\label{DSVerifier_process}
\end{figure*}

@@

Given a model for a plant for which to synthesize a controller,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and a transfer
function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
of the controller to be synthesized (step C).  Finally DSVerifier builds an
intermediate ANSI-C code for the digital system implementation, which is used as
input for the controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
(CEGIS) module, where the controller is marked as input variable to synthesize.
The properties specified in the ANSI-C code model can only be satisfied if CEGIS
synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
counterexample-guided refinement process which is explained in detail in
section~\ref{synthesiser-general}. A successful synthesis result is reported if
CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
the ANSI-C code model guarantees that a synthesized solution is complete
and sound with respect to stability property $\phi$, since it does not depend on
system inputs and outputs.  In the case of stability, the specification $\phi$
consists in a number of assumptions on the polynomial coefficients, following
Jury's Criteria, as well as the restrictions set in the representation of these
coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

@@

@@

Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant $\hat{G}(z)$, and a discretising function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
\end{align}
we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=\hat{G}(z)+\Delta{G}_b(z)=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
% denoted by $\mathfrak{G}(z)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustrative Example} \label{sec:running-ex}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

\subsubsection{Program synthesis for the illustrative example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. Here, \textit{Plant} is the discrete or 
continuous plant model, \textit{Benchmark} is the name of the employed benchmark,
\textit{I} and \textit{F} represent the number of integer and fractional bits of the 
stable controller, respectively, while \textit{Time} represents the total time 
(in seconds) to synthesise a stable controller for the given plant.

For the majority of our benchmarks, the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
back-end.

>>>>

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{C_n(z)}{C_d{z}}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{G_n(z)}{G_d{z}}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the controller's coefficients;  
similarly $\vec{b}$ and $\vec{a}$ encompass the plant's coefficients;  
and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by additive terms, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfil this property in our implementation).

In order to simplify the notations in this paper, we will use a notation based on the coefficients of the polynomials.
Let $\mathcal{P}^{N}$ be a polynomial domain of order $N$
Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. There is a vector of coefficients 
\begin{equation}
\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
with uncertainty
\begin{equation}
\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.
In the following we may use either notation to represent the functions $G(z)$, $C(z)$, and their respective uncertainties.\\

%\begin{equation}
%\Delta{\vec{p}}=\begin{bmatrix}
%\hat{b_{0}} - b_{0}\\
%\hat{b_{1}} - b_{1}\\
%\vdots \\
%\hat{b}_{M_G} - b_{M_{G}}\\
%\hat{a_{0}} - a_{0}\\
%\hat{a_{1}} - a_{1}\\
%\vdots\\
%\hat{a}_{N_G} - a_{N_{G}}\\
%\end{bmatrix}=\begin{bmatrix}
%\vec{\hat{b}}\\
%\vec{\hat{a}}
%\end{bmatrix}-\begin{bmatrix}
%\vec{b}\\
%\vec{a}
%\end{bmatrix}
%\label{eq:uncertainty}
%\end{equation}

A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta \vec{G}_{P}^s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta \vec{G}_{P}$
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$. The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q},
\end{equation}
where $\Delta \vec{G}_{P}$ is the term that corresponds to the parametric uncertainties and $\Delta \vec{G}_{Q}$ is the term that reflects the quantisation effects on the plant model. %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

@@

In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta \vec{G}(z)$ and the FWL effects on controller ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

@@

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab} 
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q}\Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if: 
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{DSVerifier Verification Flow.}
\label{DSVerifier_process}
\end{figure*}

@@

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $FWL$ represented by Eq.~\ref{FWL_tf} (step B) to
calculate the implementation $FWL(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
synthesise.  If any property violation is found, then
a counterexample is reported, which contains system inputs or
parametric deviations $\Delta{\vec{G}}$ that lead the system to a failure.  
This information allows the CEGIS module to refine its search for a stable
controller, which we explain in detail in section~\ref{synthesiser-general}.
A successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example} \label{sec:running-ex}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ stabilizes the closed-loop
system for the discrete plant model $G(z)$.  However, if implementation
aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

@@

Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant $\hat{G}(z)$, and a discretising function
\begin{align}
\small
\label{FWL_tf}
&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
\end{align}
we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_P{\vec{G}}+\Delta_b{\vec{G}}.
\end{align}
where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{\vec{G}}=\Delta_P{\vec{G}}+\Delta_b{\vec{G}}$.  % Since this value is
% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
% denoted by $\mathfrak{G}(z)$.

@@

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
back-end.
